
\subsection{Test Plan Template}
Game Development International Ltd 2D game 
\subsection{Prepared by }


\begin{enumerate}
  \item Tomas O'Malley
  \item John Smith 
	\item Laine Louhglin 
	\item Tyler Durden 


\end{enumerate}


Welcome to my Test case documentation for the latest game developed by Game Development International Ltd .
The company provided me with a short brief informing me on the features/fundamentals to their new game title.
The product developed by  Game Development International Ltd is a 2D side scrolling platformer which borrows
behaviors from other titles such as 'Shovel knight' to 'Skyrim'. Here are a list of the characteristics/functions
set in their title.

\centerline{Game fundamentals}

\begin{enumerate}
  \item Allow the player to control a specific character, that has an important
fictional/narrative role.
  \item Have game statistics and/or relational attributes with other game objects, enemies,
and/or the player character.

\item Allow the player to take on and navigate the levels using an easy-to-use user
interface.

\item Have obstacles that the player must overcome, such as enemies and bosses.
\end{enumerate}

The game holds a rich number of features and should give me the opportunity to create lots of different tests.Game testing is a huge part of our teams experience and we will apply the different methodologies to test and document their Product.Overall we were happy with the game Design Document provided by'Game Development International Ltd' which my whole team studied. Exclusive access to the game  allowed to Alpha test the game.