<<<<<<< HEAD
=======

>>>>>>> 1b7c0c4794a779eca78df872f86f0140afaaae54
\subsection{Schedule}

Scheduling in project management is the listing of activities, deliverables, and milestones within a project. A schedule also usually includes the planned start and finish date, duration, and resources assigned to each activity. Effective project scheduling is a critical component of successful time management.

Scheduling was a very difficult area to manage when testing their product. We had to create an
incremental approach starting with the bare bones of the Product and working from the ground up
e.g testing the transition from Start menu to the in-game. Underneath are Schedules created during
testing.	


\begin{center}
\centerline{Test Plan}
\end{center}
The overall testPlan was successful and we did not have to change many of the milestones.THe test plan set a pace for the team to work at and worked very well in our agile development approach.The product and test plan was a success



\begin{center}
\centerline{Test Cases}
\end{center}
The overall test cases created by developers were solid and successful.Near all components were tested and only a few minor bugs were not resorted.


\begin{center}
\centerline{Test Incident Reports}
\end{center}
The test incident Reports were created by nearly all developers when an issue was incountered.There was a template .csv sent to all users to doocument their bugs to.This report summarised bugs and was informative and beneficial to the team.



\begin{center}
\centerline{Test Summary Reports}
\end{center}
The Test Summary Reports were created by the Managers and dispersed to the whole team at the end of sprints or milestones.We found the informative summary report straight to the point and informed the entire team on their strengths and their weaknesses.
