\subsection{Unit Testing}
Unit Testing is a level of software testing where individual units/components of a software are tested. A unit is the smallest testable part of any software. It usually has one or a few inputs and usually a single output. In procedural programming, a unit may be an individual program, function, procedure,etc.

\subsection{System and Integration Testing}
System Integration Testing is defined as a type of software testing carried out in an integrated hardware and software environment to verify the behaviour of the complete system.It is testing conducted on a complete, integrated system to evaluate the system's compliance with its specified requirement.
\subsection{Performance and Stress Testing}
Performance testing is carried out to check the system's performance under varying loads.Stress testing is carried out to check the behaviour of the system under the sudden increased load of the system or software application. It only checks the stability of the system or software application.
\subsection{User Acceptance Testing}
User acceptance testing (UAT) is the last phase of the software testing process. During UAT, actual software users test the software to make sure it can handle required tasks in real-world scenarios, according to specifications
\subsection{Batch Testing}
Batch testing is a comprehensive test on your current trained model to measure its performance in LUIS. The data sets used for batch testing should not include example utterances in the intents or utterances received from the prediction runtime endpoint.\subsection{Automated Regression Testing}
Regression Testing is defined as a type of software testing to confirm that a recent program or code change has not adversely affected existing features. Regression Testing is nothing but a full or partial selection of already executed test cases which are re-executed to ensure existing functionalities work fine
\subsection{Beta Testing}
A beta test is a type of testing period for a computer product prior to any sort of commercial or official release. Beta testing is considered the last stage of testing, and normally involves distributing the product to beta test sites and individual users ("beta testers") outside the company for real-world exposure.