\subsection{Schedule}



A scrum meeting was organized and all members involved in testing or management attendance were mandatory.We mapped out an Agile Development Plan, working in work periods named 'sprints' essentially a sprint is a focus point for some time.\


A milestone is a significant event in the course of a project that is used to give visibility of progress in terms of achievement of predefined milestone goals. Failure to meet a milestone indicates that a project is not proceeding to plan and usually triggers corrective action by management.\\


Underneath is the testing schedule outlying the timing and milestones approved by our Scrum master.\\


\centerline{ The Testing Schedule}

\begin{enumerate}
   \item Month 1    : Enviroment Set Up 
   \begin{itemize}
     \item Testers will set up their environment for concurrent testing of the game. All developers will successfully loaded the 2d game on their company machine alongside big tracking software Bugzilla and Selenium for automated testing.
  
   \end{itemize}
  
  \item Month 2  : Bug Testing
   \begin{itemize}
     \item Each developer has received their testing ground e.g integration testing, Back-end, front-end testing. Developer approaches software with different strategies and successfully finds issues/bugs to report.
   \end{itemize}

     \item Month 3   : Bug Repository
   \begin{itemize}
     \item After a month of testing all bugs are documented inside of a repository alongside information such as its severity, component, developer, date and time, etc.

  
   \end{itemize}



 \item Month 4  : Alpha Testing
   \begin{itemize}
 	\item Management will organize outside users to play the  2D game to simulate a public release without releasing it to the public. The Player's impressions recorded and the product is documented and reported to developers.

 	 \end{itemize}



 \item Month 5 : Management Meeting
   \begin{itemize}
  \item Management will organize a meeting with the company 'Game Development International Ltd ' and discuss the statistics/discoveries and answer any questions the company has about the current state of the game.

   \end{itemize}

 	 \end{enumerate}
