\subsection{The Tools}


A program used for software development or system maintenance. Virtually any program
or utility that helps programmers
or users develop applications or maintain their computers can be called a tool.
The Tools used during testing are as follows :

\begin{enumerate}
   \item Bugzilla - Bug Report Tool
   \begin{itemize}
     \item Bugzilla is a web-based general-purpose bug tracking system and testing tool originally developed and used by the Mozilla project
     , and licensed under the Mozilla Public License.

      \item This bug reporting has been a go to for our company and we will not be changing as its an industry standard.
   \end{itemize}
   \item Selenium (software) - Automated Testing
   \begin{itemize}
     \item Selenium is a portable framework for testing web applications. Selenium provides a playback tool for authoring
      functional tests without the need to learn a test scripting language.

<<<<<<< HEAD
         \item We found our development team was very pleased with the product. The documentation online was very clear and can be also run in browsers which is a bonus for our web-developers.
=======
         \item We found our development team were very pleased with the product.The documentation online was very clear and can be also ran in browsers which is an added bonus for our  web-developers.
>>>>>>> 1b7c0c4794a779eca78df872f86f0140afaaae54
   \end{itemize}

   \item  LaTeX - Documentation System
   \begin{itemize}
     \item LaTeX is a document preparation system. When writing, the writer uses plain text as opposed to the formatted text found in "What You See Is What You Get"
      word processors like Microsoft Word, LibreOffice Writer, and Apple Pages.


<<<<<<< HEAD
       \item Each developer was required to upload a .pdf outlying their discoveries throughout the week and this open-source Tex editor was suitable. It is cross-platform (Mac, Windows, Linux) so our developers on other platforms had no issues installing. We may consider Microsoft Word in the future due to its steep learning curve.
=======
       \item Each developer was required to upload a .pdf outlying their discoveries throughout the week and this open source Tex editor was suitable.It is cross Platform (Mac,Windows,Linux) so our developers on other platforms had no issues installing.We may consider microsoft Word in future due to its steep learning curve.
>>>>>>> 1b7c0c4794a779eca78df872f86f0140afaaae54
   \end{itemize}


    \item  Microsoft Teams - Online Management Platform
   \begin{itemize}
     \item Microsoft Teams is a persistent chat-based collaboration platform complete with document sharing, online meetings, and many more extremely useful features for business communications. Having an excellent team space is key to being able to make creative decisions and communicate with one another.


<<<<<<< HEAD
      \item The whole team must be connected 24/7 and we found this platform suited our criteria 1. Responsive 2.Private Chatting 3.Instant Messaging. We will use this platform again in the future to monitor our workplace/employee's productivity.
   \end{itemize}




 \item  GitHub  - Version Control
   \begin{itemize}
     \item GitHub is a Git repository hosting service, but it adds many of its own features. While Git is a command line tool, GitHub provides a Web-based graphical interface. It also provides access control and several collaboration features, such as a wikis and basic task management tools for every project


      \item The whole team must use GitHub in case the newest installment in testing breaks the entire product.GitHub allowed us to collaborate on our code and work in parallel.
   \end{itemize}


=======
      \item The whole team must be connected 24/7 and we found this platform suited our criteria 1.Responsive 2.Private Chatting 3.Instant Messeging .We will use this platform again in the future to monitor our workplaces/employees productivity
   \end{itemize}


>>>>>>> 1b7c0c4794a779eca78df872f86f0140afaaae54
\end{enumerate}


